19Q2

### 2019-06-05 19Q2.Rmd
update Rmd

# Edit direction column
g2p <- add_column(g2p, Direction_Curated = NA, .after = "Direction")
g2p$Direction_Curated <- ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "resist")[,1]), "resistance", ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "sensitive|sensitivity|responsive")[,1]), "sensitivity", "none"))

@@

# Select columns for maf_changes_df
maf_changes <- select(maf_raw, Gene, DepMap_ID, Protein_Change) %>% drop_na(Protein_Change) %>% filter(Protein_Change != "" & Gene %in% g2p_genes)
maf_changes <- unique(maf_changes)
maf_changes$Protein_Change <- gsub(pattern = "^p.", replacement = "", x = maf_changes$Protein_Change)
maf_changes$Keep <- ifelse(!is.na(str_match(string = maf_changes$Protein_Change, pattern = "[A-Z][0-9]+([A-Z]|[*])")[,1]), "Yes", "No")
maf_changes_df <- filter(maf_changes, Keep == "Yes")
maf_changes_df$Keep <- NULL
maf_changes_df$Gene_Protein_Change <- with(maf_changes_df, paste0(Gene, ":", Protein_Change))
saveRDS(maf_changes_df, "./data_munging/19Q2/maf_changes_df_19Q2.rds", compress = "xz")

@@

Load Rds:
```{r load_omics_rds}
maf_df <- readRDS("./data_munging/19Q2/maf_df_19Q2.rds")
cn_melt <- readRDS("./data_munging/19Q2/cn_melt_19Q2.rds")
ge_melt <- readRDS("./data_munging/19Q2/ge_melt_19Q2.rds")
```

@@

```{r load_mut_wilcoxon_rds}
g2p_mut_4merge <- unique(select(g2p_mut, Drug_Gene, Direction_Curated))
g2p_mut_4merge$Direction_Numeric <- as.numeric(g2p_mut_4merge$Direction_Curated)

@@

ccle_signif_dg <- readRDS("./data_munging/rds/ccle_signif_dg.rds")
ccle_signif_g2p_dg <- readRDS("./data_munging/rds/ccle_signif_g2p_dg.rds")
# ccle_signif_g2p_dg <- merge(ccle_signif_g2p_dg, g2p_mut_4merge, by = "Drug_Gene", all.x = TRUE)
# ccle_signif_g2p_dg$Direction_Numeric <- ifelse(is.na(ccle_signif_g2p_dg$Direction_Numeric), 4, as.numeric(ccle_signif_g2p_dg$Direction_Numeric))
ccle_signif_dgl <- readRDS("./data_munging/rds/ccle_signif_g2p_dgl.rds")

# ctrp_signif_g <- readRDS("./data_munging/rds/ctrp_signif_dg.rds")
ctrp_signif_g2p_dg <- readRDS("./data_munging/rds/ctrp_signif_g2p_dg.rds")
# ctrp_signif_g2p_dg <- merge(ctrp_signif_g2p_dg, g2p_mut_4merge, by = "Drug_Gene", all.x = TRUE)
ctrp_signif_dgl <- readRDS("./data_munging/rds/ctrp_signif_g2p_dgl.rds")

# gdsc_signif_g <- readRDS("./data_munging/rds/gdsc_signif_dg.rds")
gdsc_signif_g2p_dg <- readRDS("./data_munging/rds/gdsc_signif_g2p_dg.rds")
# gdsc_signif_g2p_dg <- merge(gdsc_signif_g2p_dg, g2p_mut_4merge, by = "Drug_Gene", all.x = TRUE)
gdsc_signif_dgl <- readRDS("./data_munging/rds/gdsc_signif_g2p_dgl.rds")
```

>>>>

# Edit direction column
g2p <- add_column(g2p, Direction_Curated = NA, .after = "Direction")
g2p$Direction_Curated <- ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "resist|adverse|unfavorable")[,1]), "resistance", ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "sensitive|sensitivity|responsive|better")[,1]), "sensitivity", "none"))

# Edit mutation column
g2p <- add_column(g2p, Mutation_Curated = NA, .after = "Mutation")
g2p$Mutation_Curated <- gsub("u'|'| |,|\\[|\\]", "", g2p$Mutation)
g2p$Mutation_Curated <- ifelse(g2p$Mutation_Curated == "", str_match(string = g2p$Feature.Names, pattern = "^[A-Z][0-9]+([A-Z]|[*])| [A-Z][0-9]+([A-Z]|[*])|:[A-Z][0-9]+([A-Z]|[*])")[,1], as.character(g2p$Mutation_Curated))
g2p$Mutation_Curated <- gsub(":| |c\\..*", "", g2p$Mutation_Curated)
g2p$Mutation_Curated <- ifelse(!is.na(str_match(string = tolower(g2p$Mutation_Curated), pattern = "exon|expression|frameshift|fusion|methylation|mutation")[,1]), NA, as.character(g2p$Mutation_Curated))
g2p$Mutation_Curated <- gsub("^([0-9]+)([A-Z])$", "\\2\\1\\2", g2p$Mutation_Curated)
g2p$Mutation_Curated <- gsub("^([A-Z])([0-9]+)$", "\\1\\2\\1", g2p$Mutation_Curated)
g2p <- add_column(g2p, Gene_Protein_Change = NA, .after = "Mutation_Curated")
g2p$Gene_Protein_Change <- ifelse(!is.na(g2p$Gene) & !is.na(g2p$Mutation_Curated), paste0(as.character(g2p$Gene), ":", as.character(g2p$Mutation_Curated)), NA)

@@

# Select columns for maf_changes_df
maf_changes <- select(maf_raw, Gene, DepMap_ID, Protein_Change) %>% drop_na(Protein_Change) %>% filter(Protein_Change != "" & Gene %in% g2p_genes)
maf_changes <- unique(maf_changes)
maf_changes$Protein_Change <- gsub(pattern = "^p.", replacement = "", x = maf_changes$Protein_Change)
maf_changes$Gene_Protein_Change <- with(maf_changes, paste0(Gene, ":", Protein_Change))
saveRDS(maf_changes, "./data_munging/19Q2/maf_changes_df_19Q2.rds", compress = "xz")

@@

Load Rds:
```{r load_omics_rds}
maf_df <- readRDS("./data_munging/19Q2/maf_df_19Q2.rds")
maf_changes_df <- readRDS("./data_munging/19Q2/maf_changes_df_19Q2.rds")
cn_melt <- readRDS("./data_munging/19Q2/cn_melt_19Q2.rds")
ge_melt <- readRDS("./data_munging/19Q2/ge_melt_19Q2.rds")
```

```{r}
test <- filter(maf_changes_df, Gene_Protein_Change %in% unique(g2p_mut$Gene_Protein_Change))
```

@@

```{r load_mut_wilcoxon_rds}
g2p_mut_4merge <- unique(select(g2p_mut, Drug_Gene, Direction_Curated))
test <- g2p_mut_4merge %>% filter(Direction_Curated != "none") %>% count(Drug_Gene) %>% filter(n == 2)
extended_mut_ht_dg <- unique(as.character(test$Drug_Gene))

@@

ccle_signif_dg <- readRDS("./data_munging/rds/ccle_signif_dg.rds")
ccle_signif_g2p_dg <- readRDS("./data_munging/rds/ccle_signif_g2p_dg.rds")
ccle_signif_dgl <- readRDS("./data_munging/rds/ccle_signif_g2p_dgl.rds")

# ctrp_signif_g <- readRDS("./data_munging/rds/ctrp_signif_dg.rds")
ctrp_signif_g2p_dg <- readRDS("./data_munging/rds/ctrp_signif_g2p_dg.rds")
ctrp_signif_dgl <- readRDS("./data_munging/rds/ctrp_signif_g2p_dgl.rds")

# gdsc_signif_g <- readRDS("./data_munging/rds/gdsc_signif_dg.rds")
gdsc_signif_g2p_dg <- readRDS("./data_munging/rds/gdsc_signif_g2p_dg.rds")
gdsc_signif_dgl <- readRDS("./data_munging/rds/gdsc_signif_g2p_dgl.rds")
```
